Trail Saving on Backtrack

### 2020-02-29 paper.tex
final

\section{Experiments and Results}
We implemented our techniques in two different SAT solvers, MapleSAT
and Cadical, both of which have finished at or near the top of SAT
competitions for the past several years
\cite{Heule2018ProceedingsOS,Heule2019ProceedingsOS}. We then ran each
solver on the 800 total benchmark instances used in the main tracks of
the 2018 and 2019 SAT competitions. The experiments were executed on a
cluster of 2.7 GHz Intel cores with 5000 seconds CPU time and 7 GB
memory limits for each instance. We chose not to output or verify the
proofs generated by any of the solvers. The Par-2 scores obtained and
total instances solved by each solver are reported in
Figures~\ref{fig:cadicalNew}, \ref{fig:cadicalOld}, and
\ref{fig:maple}.

@@

In Figure~\ref{fig:props} we plotted the propagations per second for
each instance with and without trail saving enabled in cadical. With
trail saving enabled about 1.87 million propagations per second occur,
and without trail saving about 1.80 million propagations per second
occur. The graph further illustrates that the majority of the time
cadical with trail saving enabled will propagate literals faster than
cadical without trail saving enabled, as we predicted would be the
case earlier in this paper.

@@

@@

There are many avenues that can be pursued in future work, such as
using the saved trail to help make inprocessing techniques faster or
using the saved trail to learn a multiple clauses from a single
conflict. It is also possible to combine trail saving with
chronological backtracking if one is willing to break the traditional
invariants of CDCL, but it would require further work to determine
whether or not this would be useful and how to best approach it.

>>>>

\section{Experiments and Results}
We implemented our techniques in two different SAT solvers, MapleSAT
and Cadical, both of which have finished at or near the top of SAT
competitions for the past several years
\cite{Heule2018ProceedingsOS,Heule2019ProceedingsOS}. We then ran each
solver on the 800 total benchmark instances used in the main tracks of
the 2018 and 2019 SAT competitions. The experiments were executed on a
cluster of 2.7 GHz Intel cores with 5000 seconds CPU time and 7 GB
memory limits for each instance. We chose not to output or verify the
proofs generated by any of the solvers. The Par-2 scores obtained and
total instances solved by each solver are reported in
Figures~\ref{fig:cadicalNew}, \ref{fig:cadicalOld}, and
\ref{fig:maple}. We also show the cactus plots of the new version of
cadical in Figure \ref{fig:cactus_cadical} and MapleLCMDist in Figure
\ref{fig:cactus_maple}.

@@

In Figure~\ref{fig:props} we plotted the propagations per second for
each instance with and without trail saving enabled in cadical (rounded
to the nearest 0.1 million). Only
the 506 instances solved by both solvers are plotted. With trail saving
enabled, 213 instances had more propagations per second, 149 instances
had less propagations per second, and 144 instances had about the same
number of propagations per second. On the graph, points above the diagonal
represent instances where trail saving had faster propagation. The
graph illustrates that the majority of the time
cadical with trail saving enabled propagated literals faster than
cadical without trail saving enabled, as we predicted would be the
case earlier in this paper.

@@

\begin{figure}\centering\includegraphics[scale=0.65]{figures/cactus_maple_new.pdf}\caption{\small{Cactus plot for MapleLCMDist comparing standard non-chronological backtracking to \cbt and various configurations of trail saving. The first 300 problems were solved in less than 600 seconds, so that part of the plot is truncated.}}\label{fig:cactus_maple}\end{figure}

@@

There are many avenues that can be pursued in future work, such as
using the saved trail to help make inprocessing techniques faster or
using the saved trail to learn multiple clauses from a single
conflict. It is also possible to combine trail saving with
chronological backtracking if one is willing to break the traditional
invariants of CDCL, but it would require further work to determine
whether or not this would be useful and how to best approach it.
